Dark matter halo concentrations with a bayesian approach

### 2014-09-13 paper/article.tex
added new line

\subsection{Comparison against other methods}
We compared this method against two methods: The first one consists in using shells for estimating the density in function of the radius and using the same MCMC method for fitting and the second one consists in using the circular velocity $V(r)=\sqrt{GM(<r)/r}$ and the relation for the NFW profile
\begin{equation}
\frac{V_{max}}{V(r_{v})} = \sqrt{\frac{0.216c}{M(r_{v};c)}}
\end{equation}
Where $V_{max}$ is the maximum velocity, to find the value of the concentration.

We tested the three methods using the same data from the Mock Halos test. In order to see the accuracy of each method depending on the number of particles we define

@@

@@

The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles.
\subsection{Implication for comparisons against observations}
FIXME: Ask to Jaime

>>>>

\subsection{Comparison against other methods}
We compared this method against two methods: The first one consists in using shells for estimating the density in function of the radius and using the same MCMC method for fitting and the second one consists in using the circular velocity $V(r)=\sqrt{GM(<r)/r}$ and the relation for the NFW profile
\begin{equation}
\frac{V_{max}}{V(r_{v})} = \sqrt{\frac{0.216c}{M(r_{v};c)}}
\end{equation}
Where $V_{max}$ is the maximum velocity, to find the value of the concentration. We tested the three methods using the same data from the Mock Halos test. In order to see the accuracy of each method depending on the number of particles we define

@@

We also used these three methods to obtain the concentration for each halo in miniMDR1 and compared the results. As can be seen in the Figures \ref{fig:density-mass}, \ref{fig:density-velocity} and \ref{fig:velocity-mass} the three methods show mutually consistent results. However it can be inferred that the concentration values ​​obtained by the method of circular velocity are higher than those obtained by our method, and also the values ​​obtained by the density method are generally below the results of our method.

@@

The bold lines in Figure \ref{fig:concentrations} corresponds to the median and the thinner lines corresponds to the quartiles. Showing that our method has values ​​ranging from those obtained from the other two methods.
\subsection{Implication for comparisons against observations}
FIXME: Ask to Jaime
